---
title       : Prediction Height Application
subtitle    : Predict child's height from parent's height
author      : David Ibáñez Alonso
logo        : alto_peke.gif
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [rCharts: libraries/nvd3]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Motivation and App Explanation

- We want to create an application to ``predict`` the child's height knowing the parent's height.
- We are using the data from the famous 1885 study of ``Francis Galton``, 
exploring the relationship between the heights of children and the 
height of their parents, to build our predicting model. The variables 
are the height of the adult child and the midparent height, defined as 
the average of the height of the father and 1.08 times the height 
of the mother. The units are inches. The number of cases is 928, 
representing 928 children and their 205 parents.
- As ``input`` we have the ``Parent's Height``.
- Inputs height work from `50` to `90` inches.
- As ``output`` we have the predicted ``Child's Height``.
- We have also a ``plot`` with our prediction, galton's data and the linear model we build.
- You can find the Applicatio here https://pinap.shinyapps.io/DDP_Project/


--- .class #id 

## Data Used

- We are using Galton's data from the `UsingR` library.

```{r, results='hide'}
library(UsingR)
```

```{r}
summary(galton)
```

--- .class #id

## Linear Model

```{r, echo=FALSE}
fit <- lm(child ~ parent, galton)
summary(fit)
```

--- .class #id

## Plot Data and Linear Model

```{r, fig.align='center', fig.height = 5}
plot(galton$parent, galton$child, xlab = "Parent's Height", ylab = "Child's Height", 
     pch = 16, xlim = c(50,90), ylim = c(56, 82))
abline(fit, col = "red", lwd = 4)
```
